The Surprising Runtime Fragility Found when Querying a Single Table

### 2015-05-18 testdata/chunked_column_layouts/draft.tex
!

\begin{figure}[!h]
\vspace{-5pt}
\centering
\includegraphics[width=0.48\textwidth]{pdf/problem_bests_plot.pdf}
\vspace{-20pt}
\caption{Best layouts and their query times. Drilled-down along machine, schema, and query.}  
\label{fig:problem_bests_plot}
\vspace{-10pt}
\end{figure}

>>>>

\begin{figure}[!h]
\vspace{-5pt}
\centering
\multiplot[
width=0.48\textwidth, 
height=0.3329\textwidth, 
charttype=scatter,
xunit={Best layouts}, 
yunit={Average query time [seconds]}, 
xCount=1, yCount=4, 
yValues={[ 
"cpuarchitecture='Nehalem'", 
"cpuarchitecture='Westmere'", 
"cpuarchitecture='Sandy Bridge'", 
"cpuarchitecture='Ivy Bridge'" 
]}, 
xValues={[
"querytext='SELECT MIN(a+b) FROM t' AND tableschema='(char a, char b)'"%, 
%"querytext='SELECT SUM(a*b) FROM t' AND tableschema='(char a, char b)'", 
%"querytext='SELECT MIN(a+b) FROM t' AND tableschema='(int a, int b)'", 
%"querytext='SELECT SUM(a*b) FROM t' AND tableschema='(int a, int b)'", 
%"querytext='SELECT MIN(a+b) FROM t' AND tableschema='(long a, long b)'", 
%"querytext='SELECT SUM(a*b) FROM t' AND tableschema='(long a, long b)'"
]}, 
rightArr={["Nehalem", "Westmere", "Sandy Bridge", "Ivy Bridge"]}, 
topArr={[""]}, 
forceXequal, 
forceYequal, 
yFirst,
chartType=SignaturePlot,
options={
	"padding" : { "top" : 6, "right" : 8 }, 
	"axis": { 
%		"x" : { 
%			"tick" : { "values" : [0, 0.25, 0.5, 0.75, 1], "rotate" : 90 }, 
%			"min" : 0, 
%			"max" : 1, 
%			"padding" : { "left" : 0, "right" : 0 } 
%		}, 
		"y": { 
			"tick" : { "values" : [0, 0.2, 0.4, 0.6, 0.8, 1.0]}, 
			"min" : 0, 
			"max" : 1, 
			"padding" : { "top" : 0, "bottom" : 0 } 
		} 
	}, 
	"legend" : { "show" : false } 
} 
]]{}
\vspace{-20pt}
\caption{Best layouts and their query times. Drilled-down along machine, schema, and query.}  
\label{fig:problem_bests_plot}
\vspace{-10pt}
\end{figure}
